Output Summary

### 2021-09-15 03-post-process/output-plots.Rmd
Don't summarize diagnostics for sig_inits
Fixing its value at 0.3

# Initial adult recruitment
L1 = "Initial Adult Recruitment"
L2 = c("Mean", "Process SD", "Realized")
match = c("mu_init_recruits[.]", "sig_init_lrecruits[.]", "^init_recruits[.+,.]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

>>>>

# Initial adult recruitment
L1 = "Initial Adult Recruitment"
L2 = c("Mean", "Realized")
match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
